Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-19 Draft.Rmd
Update Draft.Rmd

## Models 
```{r Linear Regression}
# Create the recipe for all models
rec <- origin %>% 
    recipe(value ~ lat + lon + state) 
# rec

@@

# Check performance of lin. regr. model on the complete training data
res1 %>% 
    extract_fit_engine() %>% 
    summary()

# Check  lin. regr. model performance using cross-validation
folds1 <- vfold_cv(train, v = 10)
folds1
res1 <- fit_resamples(wf1, resamples = folds1)
res1 %>% 
    collect_metrics()
```
```{r kNN}
## Scale the data for k-NN model
origin_scaled <- origin %>% 
    mutate(across(-value, scale))

## Create the model
model2 <- nearest_neighbor(neighbors = 5) %>% 
    set_engine("kknn") %>% 
    set_mode("classification")

>>>>

## Models 
```{r Linear Regression}
# Create the recipe for all models
rec <- origin %>% 
    recipe(value ~ lat + lon + state)

@@

# Check performance of linear regression model on the complete training data
res1 %>% 
    extract_fit_engine() %>% 
    summary()

# Check  linear regression model performance using cross-validation
folds1 <- vfold_cv(train, v = 10)
folds1
res1 <- fit_resamples(wf1, resamples = folds1)
res1 %>% 
    collect_metrics()
```
```{r kNN}
## Scale the data for k-NN model
origin_scaled <- origin %>% 
    mutate(across(-value, scale))

## Create kNN model
model2 <- nearest_neighbor(neighbors = 5) %>% 
    set_engine("kknn") %>% 
    set_mode("classification")
